---
title: "Impact of chess elo ratings"
bibliography: references.bib
csl: apa.csl
---
# Abstract

This paper presents an empirical analysis of a dataset from Week 40 of the Tidytuesday project, which features chess games played on the Lichess platform. The study examines two hypotheses: (1) the first-move advantage, where White enjoys a higher likelihood of victory, becomes more pronounced as player ratings increase, and (2) higher-rated players are more likely to resign in losing positions than to play until checkmate.
Using R and the tidyverse ecosystem, we analyzed rated games to explore the relationships between player ratings, first-move advantage, and resignation behaviors. Our findings indicate that while the first-move advantage is evident, its impact diminishes at higher rating levels, reflecting the strategic depth and adaptability of skilled players. Similarly, higher-rated players were significantly more likely to resign in hopeless positions, underscoring their ability to evaluate positions accurately and adhere to cultural norms of sportsmanship.
This analysis provides insights into how player ratings influence chess strategies and decision-making, offering a focused exploration of key aspects of chess gameplay in an online context. The findings highlight behavioral patterns shaped by skill level, contributing to a deeper understanding of chess dynamics in modern platforms. 

# Preface

In this paper, we present a brief empirical analysis of the dataset from Week 40 of the Tidytuesday project. Tidytuesday is an open-source initiative within the R community that encourages participants to conduct small-scale analyses and create visualizations based on datasets provided weekly.

The Week 40 dataset originates from a popular online chess platform and includes a subset of games played on the site.

This work was completed as part of the 3-day seminar "Data Literacy in R" at KIT. As the contributors are neither experts in data science nor chess, we advise against using or referencing this paper in academic or professional contexts.

# 1. Introduction

Chess, a game with a history spanning over 1,500 years, underwent significant evolution before reaching its standardized form in the 19th century. These standardized rules facilitated national and international competition and laid the groundwork for the analytical exploration of chess strategy and fairness. Despite advancements in chess theory and the advent of modern chess engines that outperform even the best human players, questions surrounding the inherent fairness of chess persist. A central focus of these debates is the so-called "first-move advantage," which has been widely acknowledged by players and theorists since the late 19th century [@fairerchess].
 
The first-move advantage refers to the slight edge enjoyed by White, who always makes the opening move. Wilhelm Steinitz, the first World Chess Champion, was among the earliest to speculate that this advantage might render chess a "solved" game, leading to strategic stagnation [@pandolfini]. Empirical studies support this notion, showing that White's win rate in professional games consistently exceeds Black's by approximately 3 to 5 percentage points. Modern chess engines, such as Stockfish, further corroborate this advantage. Even in games between equally matched engines operating under optimal conditions, White wins slightly more often than Black, though the majority of games end in a draw [@WikipediaFirstMoveAdvantage].
 
A key element of understanding chess outcomes and strategies lies in the rating systems used to measure player skill. The Elo system, introduced in 1950 by Arpad Elo, revolutionized chess by providing a numerical framework to evaluate player strength. This system assumes a normal distribution of player skill and predicts game outcomes using a logistic function of the rating difference [@elo1978rating]. While effective, the Elo system has limitations, particularly in accounting for fluctuations in player performance over time. To address these issues, the Glicko and Glicko-2 systems were later developed by Mark Glickman (1995). These systems introduced the concept of "rating deviation" (RD) to measure the confidence in a player’s rating and adapted to the dynamic nature of player activity [@glicko].
 
Platforms like Lichess and Chess.com have adopted these advanced systems, with Lichess utilizing Glicko-2 [@lichessRatings] and starting new players at a baseline rating of 1500. In contrast, Chess.com starts players at 1000, reflecting differences in implementation that make direct comparisons between platforms challenging [@chesscomRatings]. Beyond measuring skill, these systems influence player behavior, strategy, and even tournament pairings, underscoring their central role in modern chess.

Another funamental aspect of chess is Time control, which ensures that matches conclude within a reasonable timeframe[@timecontrol]. By establishing strict limits on the time each player can use, time controls help prevent games from dragging on and promote a fair pace of play.

Game clocks enforce time controls, with two timers—one for each player—operating independently. When a player makes a move, they press a button on the clock to pause their own timer and start their opponent’s. This setup ensures that both players have an equal opportunity to manage their allotted time.

Time control formats vary widely in tournaments. Some matches employ a "sudden death" system, where each player has a fixed amount of time to complete all their moves. Others use incremental time controls, which add extra seconds or minutes to a player’s clock with each move, helping to alleviate intense time pressure in longer games. Another popular variation is the "delay" system, which provides a short buffer period before the main timer begins to count down.

If a player exceeds the allotted time, the penalty is typically a loss, regardless of the game’s position. This rule introduces a strategic challenge, as players must balance their focus between making optimal moves and managing their time effectively.

"Time pressure" refers to the situation where a player has very little time remaining to complete their moves. This condition often leads to rushed decisions and errors, significantly affecting the quality of play. For competitive players, the ability to handle time pressure is a critical skill, requiring a balance between careful analysis and adherence to the constraints of the clock.

By integrating time controls, chess tournaments foster a structured and competitive environment that tests a player’s strategic thinking, tactical skills, and ability to perform under pressure. Effective time management often becomes a decisive factor, distinguishing top players from the rest.

The first hypthesis explored in this paper is whether the first-move advantage becomes more pronounced as player ratings increase. The hypothesis is grounded in the assumption that higher-rated players, who tend to make fewer mistakes, are better equipped to exploit White’s initiative [@ribeiro2013move]. This paper analyzes empirical data from online chess games to examine this relationship.
 
In addition to the first-move advantage, this paper investigates a second hypothesis: that higher-rated players are more likely to resign in losing positions rather than play to checkmate. This behavior reflects a cultural norm in professional chess, where resigning is often considered an acknowledgment of the opponent's skill and a mark of respect [@fairerchess]. The analysis aims to determine whether this pattern is evident in online chess games and whether it correlates with player ratings.
 
By leveraging data from the Tidytuesday community project [@TidyTuesday], this study provides a focused examination of these hypotheses. While the dataset offers only a snapshot of games played on the Lichess platform, it serves as a basis for exploring the influence of player ratings on key aspects of chess strategy and outcomes.

# 2. Methods
For the evaluation we used RStudio with the tidyverse ecosystem. Our dataset is sourced from
week 40 of the tidy tuesday community project. Although bigger datasets are available at
the [lichess database](https://database.lichess.org/), we decided to stick with the much 
simpler and easier to use datasets published by the tidy tuedays community.

To reproduce our results we advise using the R 4.4.2 and 
packages with the same version.

| Package Name | Description | Version |
| :- | :- | -: |
| tidyverse | Opinionated collection of R packages | 2.0.0 |
| dplyr | data manipulation | 1.1.4 |
| readr | reading csv files | 2.1.5 |
| weights | weighted correlation and interpolation | 1.0.4 |
| easypackages | R package managing | 0.1.0 |

All of our source code is publically available on
[github](https://github.com/kistenklaus/tidytueday-submission) or 
visualized in a notebook [here](source.html).

To ensure our Dataset reflects our assumptions from the introduction such as the first-move advantage we start by performing a preleminary analysis.

# 3. Exploring the Dataset

In this section we want to provide a short look at the lichess dataset to 
evaluate its completeness. 
In the introduction, we showed that in  over the board games it is generally an accepted truth that 
the player with the white pieces has an advantage, we now aim to verify that this 
assumption is also true for our lichess dataset. 
To evaluate this assumption we simly compute the average win percentage across 
all rated games in our dataset.
```{r message=FALSE, echo=FALSE, fig.align='center'}
rm(list = ls())
library(remotes)
options(repos = "https://cloud.r-project.org/")
options(scipen = 999)
if (!require("easypackages")) {
  install.packages("easypackages")
  library(easypackages)
} else {
  library(easypackages)
}
packages(
  "tidyverse",
  "tidytuesdayR",
  "dplyr",
  "readr",
  prompt = FALSE
)

tuesday_chess <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-10-01/chess.csv')

# Filter and select relevant columns
chess <- tuesday_chess %>%
  filter(rated == TRUE) %>% # Fix logical comparison
  select(winner)

# Converts the chess table of column winner into a 3 columns, which count the
# amount of times a game ended with white winning, black winning or
# the game beeing drawn
outcomes <- table(chess$ winner)

outcome_percentages <- prop.table(outcomes) * 100

pie(outcome_percentages,
    labels = paste(
      names(outcome_percentages),
      "(", round(outcome_percentages, 1), "%)", sep = ""),
    col = c("lightblue", "lightgreen", "lightcoral"),
    main = "Lichess dataset rated games outcome")
```

*The full source code is available [here](source.html)*

This short preliminary analysis shows that the first move advantage is clearly
present in our small lichess data set, which might indicate that the subsection of 
overall games played on lichess represented in the data set if not screwed 
in this regard.


Next up in our background section we found that lichess is using the Glicko II system, 
therefor our rating distribution across games should represent a normal distribution 
around the average rating of 1500, we can verify this assumption by 
looking at the ratings of all players in our data set.
For this we have to be careful to not count ratings of players with more games,
twice as those are likely to be rated higher. Luckily our data set contains a 
player id which we can use to only count the ratings of players once.
If multiple games for a single player exists we can pick either the most recent rating 
or the average rating across games, as it is unclear to us if averaging the 
ratings might lead to a statitical error we choose to select the rating of the most 
recently played game.
``` {r message=FALSE, echo=FALSE, fig.align='center'}
rm(list = ls())

library(remotes)
options(repos = "https://cloud.r-project.org/")
options(scipen = 999)
if (!require("easypackages")) {
  install.packages("easypackages")
  library(easypackages)
} else {
  library(easypackages)
}
packages(
  "tidyverse",
  "tidytuesdayR",
  "dplyr",
  "readr",
  prompt = FALSE
)

tuesday_chess <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-10-01/chess.csv')

# Filter and select relevant columns
chess <- tuesday_chess %>%
  filter(rated == TRUE) %>% # Fix logical comparison
  select(white_id, white_rating, black_id, black_rating, start_time)

player_ratings <- chess %>%
  pivot_longer(
    cols = c(white_rating, black_rating),
    names_to = "pivot_label",
    values_to = "rating"
  ) %>%
  mutate(player_id = ifelse(pivot_label == "white_rating", white_id, black_id)) %>%
  select(player_id, rating, start_time) %>%
  group_by(player_id) %>%
  summarise(
    max_rating = max(rating),
    min_rating = min(rating),
    avg_rating = mean(rating),
    rating = rating[which.max(start_time)],
    games_played = n()
  ) %>%
  ungroup()

ggplot(player_ratings, aes(x = rating)) +
  geom_histogram(
    aes(y = after_stat(count) / sum(after_stat(count)) * 100),
    binwidth = 100,
    fill = "steelblue",
    color = "black",
    alpha = 0.7
  ) +
  labs(
    title = "Average Player Ratings",
    x = "Rating",
    y = "Percentage of Players"
  ) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  theme_minimal()
```

*The full source code is available [here](source.html)*

This short preliminary analysis, is yet another indicator to the completeness 
of the lichess data set, indicating that the games represented in the dataset 
do not represent any screw towards higher or lower rated games.

# 4. Results

### Hypothesis 1
To evaluate the impact of player ratings on the strength of the first-move advantage, we analyzed only rated games that did not end in a draw. Unrated games were excluded because they cannot provide a reliable basis for correlating ratings with White's winning advantage. Additionally, games that ended in a draw were omitted to focus solely on games with definitive outcomes.

White's win percentage was calculated on the filtered dataset. Next, we grouped games by similar player rating ranges and computed White's win percentage for each group. To ensure statistical significance, we considered only groups with more than 200 games.

The graph below presents the results. Each bar represents White's win percentage within a rating group, with the bar's opacity reflecting the significance of the group, proportional to the number of games played.

Additionally, a weighted linear interpolation line is shown in red. The weighted correlation between player rating and White's win percentage was calculated as -0.4312621, with a p-value of approximately 0.08.

``` {r message=FALSE, echo=FALSE, fig.align='center'}
#### Hypothesis
# 2. At lower ratings the difference between black and white is neglegible

rm(list = ls())

library(remotes)
options(repos = "https://cloud.r-project.org/")
options(scipen = 999)
if (!require("easypackages")) {
  install.packages("easypackages")
  library(easypackages)
} else {
  library(easypackages)
}
packages(
  "tidyverse",
  "tidytuesdayR",
  "dplyr",
  "readr",
  "weights",
  prompt = FALSE
)

tuesday_chess <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-10-01/chess.csv')

chess <- tuesday_chess %>%
  dplyr::filter(rated == TRUE) %>%
  dplyr::filter(winner != "draw") %>%
  dplyr::select(winner, white_rating, black_rating) %>%
  dplyr::mutate(game_rating = (white_rating + black_rating) * 0.5)

bin_size <- 100
# Correct calculation of avg_rating
white_win_data <- chess %>%
  mutate(
    avg_rating = (white_rating + black_rating) / 2,  # Average rating for grouping
    # Define breaks with "nice" round numbers
    rating_bin = cut(avg_rating,
                     breaks = seq(600, max(avg_rating, na.rm = TRUE) + bin_size, by = bin_size),
                     include.lowest = TRUE)
  ) %>%
  group_by(rating_bin) %>%
  summarise(
    white_win_rate = sum(winner == "white") / n() * 100,  # White win percentage
    total_games = n(),
    avg_rating = mean(avg_rating)  # Calculate average rating for each bin
  ) %>%
  ungroup()

white_win_data_significant <- white_win_data %>%
  filter(total_games >= 200) %>%
  mutate(rating_bin = droplevels(rating_bin))

# Convert bins to strings in the format "800-900", "900-1000", etc. without scientific notation
bins_cleaned <- gsub("\\(|\\)|\\[|\\]", "", levels(white_win_data_significant$rating_bin)) %>%
  gsub(",", "-", .) %>%
  strsplit("-") %>%
  lapply(function(x) paste0(format(as.numeric(x), scientific = FALSE, trim = TRUE), collapse = "-")) %>%
  unlist()

ggplot(white_win_data_significant, aes(x = avg_rating, y = white_win_rate)) +
  geom_col(aes(alpha = total_games), fill = "steelblue") +  # Set alpha based on total_games
  geom_hline(yintercept = 50, linetype = "dashed", color = "red") +  # Reference line at 50%
  geom_text(aes(label = total_games),
            vjust = -0.5,  # Position the text above the bars
            color = "black",
            size = 3.5) +  # Adjust text size
  geom_smooth(
    aes(weight = total_games),  # Weight the interpolation by the total number of games
    method = "lm",              # Use linear regression
    color = "darkred",          # Set line color
    se = TRUE                   # Show confidence interval
  ) +
  labs(
    title = "White Win Percentage by Rating with Weighted Interpolation",
    x = "Average Rating (binned)",
    y = "White Win Percentage (%)",
    alpha = "Total Games"  # Add legend for alpha
  ) +
  scale_x_continuous(
    breaks = white_win_data_significant$avg_rating,  # Use midpoints for breaks
    labels = bins_cleaned  # Map custom labels to the breaks
  ) +
  scale_alpha_continuous(range = c(0.5, 1)) +  # Adjust alpha scaling range
  coord_cartesian(ylim = c(40, 60)) +  # Set the visible y-axis range without clipping
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

# Compute weighted correlation on the filtered dataset
weighted_corr <- wtd.cor(white_win_data$avg_rating, white_win_data$white_win_rate, weight = white_win_data$total_games)
print(weighted_corr)
```

*The full source code is available [here](source.html)*

To investigate the influence of time control 
on the first-move advantage, 
we analyzed all rated games that did not end in a draw. 
The games were grouped by time control, 
and White's win percentage was calculated for each group.
Similar to the previous analysis, the opacity of each bar 
in the graph reflects the number of games in the corresponding
group, providing a visual representation of group
significance.

``` {r message=FALSE, echo=FALSE, fig.align='center'}
rm(list = ls())

library(remotes)
options(repos = "https://cloud.r-project.org/")
options(scipen = 999)
if (!require("easypackages")) {
  install.packages("easypackages")
  library(easypackages)
} else {
  library(easypackages)
}
packages(
  "tidyverse",
  "tidytuesdayR",
  "dplyr",
  "readr",
  "weights",
  prompt = FALSE
)

tuesday_chess <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-10-01/chess.csv')

chess <- tuesday_chess %>%
  dplyr::filter(rated == TRUE) %>%
  dplyr::filter(winner != "draw") %>%
  dplyr::group_by(time_increment) %>%
  summarise(
    white_wins = sum(winner == "white"),
    black_wins = sum(winner == "black"),
    total_games = white_wins + black_wins,
    white_win_rate = (white_wins / total_games) * 100.0,
  ) %>%
  dplyr::ungroup() %>%
  # Remove unimportant time controls
  dplyr::filter(total_games > 100) %>%
  # Sort by time controls
  tidyr::separate(time_increment, into = c("base_time", "increment"), sep = "\\+", convert = TRUE) %>%
  arrange(base_time, increment) %>%
  mutate(
    time_increment = paste0(base_time, "+", increment),
    time_increment = factor(time_increment, levels = unique(paste0(base_time, "+", increment)))
  ) %>%
  select(-base_time, -increment)



ggplot(chess, aes(x = time_increment, y = white_win_rate)) +
  geom_col(aes(alpha = total_games^(0.125), fill = "steelblue")) +
  geom_hline(yintercept = 50, linetype = "dashed", color = "red") +  # Reference line at 50%
  geom_text(aes(label = total_games),
            vjust = -0.5,  # Position the text above the bars
            color = "black",
            size = 3.5) +  # Adjust text size
  labs(
    title = "White Win Percentage by Time Increment",
    x = "Time Increment",
    y = "White Win Percentage"
  ) +
  coord_cartesian(ylim = c(40, 60)) +  # Set the visible y-axis range without clipping
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"  # Removes the legend
  )
```

*The full source code is available [here](source.html)*

### Hypothesis 2

The hypothesis that "Higher rated players are more likely to resign than to be checkmated" is supported by our analysis. To explore the impact of player ratings on game outcomes, we categorized games based on the average Elo rating of both players, dividing them into three rating brackets: Low, Medium, and High Elo. Unrated games were excluded from the analysis.

The rating categories were defined as:

    Low Elo: Average rating between 0 and 1400
    Medium Elo: Average rating between 1400 and 1600
    High Elo: Average rating above 1600

These ranges were chosen to ensure relatively equal bucket sizes for a fair comparison. Adjusting the exact boundaries would not significantly affect the findings, as the overall trend remains consistent.

The graph below illustrates the likelihood of players resigning versus being checkmated across the three Elo categories. The data shows that as average player rating increases, the tendency to resign rather than face checkmate becomes more pronounced. This behavior reflects higher-rated players' greater strategic awareness and experience, enabling them to recognize losing positions earlier and resign to save time and maintain sportsmanship.

At higher Elo levels, players are more likely to acknowledge a hopeless position and resign rather than prolong the game unnecessarily. In contrast, lower-rated players may not fully assess the irreversibility of their positions and are thus less inclined to resign.

By categorizing games this way, we gain insight into how player ratings influence decisions related to game outcomes, particularly the choice to resign.

``` {r message=FALSE, echo=FALSE, fig.align='center'}
rm(list = ls())
library(remotes)
options(repos = "https://cloud.r-project.org/")
options(scipen = 999)
if (!require("easypackages")) {
  install.packages("easypackages")
  library(easypackages)
} else {
  library(easypackages)
}
packages(
  "tidyverse",
  "tidytuesdayR",
  "dplyr",
  "readr",
  "weights",
  prompt = FALSE
)

# Load necessary libraries
library(dplyr)
library(readr)

# Load the dataset
tuesday_chess <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-10-01/chess.csv')

# Filter and select relevant columns
chess <- tuesday_chess %>%
  filter(rated == TRUE) %>% # Fix logical comparison
  select(victory_status, white_rating, black_rating)

# Get the maximum rating
white_max_rating <- max(chess$white_rating, na.rm = TRUE)
# print(white_max_rating)

black_max_rating <- max(chess$black_rating, na.rm = TRUE)
# print(black_max_rating)

# Calculate the average rating for each game and categorize
chess <- chess %>%
  mutate(
    avg_rating = (white_rating + black_rating) / 2, # Add avg_rating
    rating_category = cut(
      avg_rating,
      breaks = c(0, 1400, 1600, Inf), # Define rating bins
      labels = c("Low", "Medium", "High")
    )
  )

# View summary of rating categories
# summary(chess$rating_category)

# Group by rating category and victory status, calculate proportions
proportions <- chess %>%
  group_by(rating_category, victory_status) %>%
  dplyr::summarize(count = n(), .groups = 'drop') %>%
  group_by(rating_category) %>%
  mutate(proportion = count / sum(count))

# View the proportions table
# print(proportions)

# Load ggplot2
library(ggplot2)

# Create a bar plot of proportions with counts as labels
ggplot(proportions, aes(x = rating_category, y = proportion, fill = victory_status)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(
    aes(label = count),
    position = position_dodge(width = 0.9),
    vjust = -0.5,
    size = 3.5
  ) +
  labs(
    title = "Proportion and Count of Victory Status by Rating Category",
    x = "Rating Category",
    y = "Proportion",
    fill = "Victory Status"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14)
  )



```
*The full source code is available [here](source2.html)*

# 5. Discussion

### Hypothesis 1: The Effect of Player Ratings on the First-Move Advantage

Our analysis of games with rated players supports the hypothesis that White enjoys a first-move advantage. However, we observed that this advantage diminishes at higher rating levels. This trend aligns with existing literature that suggests higher-rated players rely less on the exact opening theory and more on their overall positional understanding. At higher levels, players tend to focus more on strategic maneuvering and the evaluation of imbalances in the position rather than memorizing specific opening lines. This allows them to outplay their opponents in complex middlegame positions, making the first-move advantage appear less pronounced.[@openingimpact]

The results show a negative correlation between player ratings and White's win percentage, which suggests that at lower ratings, players are more able to capitalize on the first-move advantage. This is consistent with the idea that at beginner or intermediate levels, players may not have a sufficient understanding of positional concepts or long-term planning, and thus, the advantage of moving first is more significant.

Another possibility could be that the player on the black side is unable to reach a position where they can outplay the player who started with White. In such cases, the disadvantaged player may rely on their opponent making a mistake, hoping for a blunder that could turn the game in their favor.

Our analysis also examined the influence of time control on White's win percentage. Time controls, especially rapid or blitz formats, can reduce the advantage traditionally associated with the first move. High-rated players might still maintain an advantage in these faster formats, but they are more likely to adapt quickly and optimize their positions with less time on the clock. This suggests that time control plays a significant role in reducing the impact of first-move advantage, as it introduces a more dynamic aspect to the game where quick decisions and tactical awareness become more important than opening preparation.

Overall, our findings reflect that as player rating increases, their focus shifts from memorizing opening moves to adapting to the overall position and strategizing based on long-term factors. This supports the notion that expert players are less reliant on opening theory and more engaged in creating favorable middlegame positions.

### Hypothesis 2: The Influence of Rating on Resignation vs. Checkmate

Our findings support the hypothesis that higher-rated players are more likely to resign in hopeless positions rather than being checkmated. This aligns with the concept of strategic awareness. As players' ratings increase, they develop a more profound understanding of when the game is essentially lost. High-rated players are better at recognizing hopeless positions and tend to resign earlier, as this is often seen as a demonstration of sportsmanship and respect for the opponent.

This behavior could be attributed to the fact that high-level players are often less concerned with prolonging games unnecessarily. Instead, they may prefer to focus on improving their performance in future games rather than wasting time in a lost position. Furthermore, expert players’ decision-making evolves such that they are more capable of evaluating the overall position rather than fixating on immediate tactical threats. This ability allows them to assess that the position is untenable earlier, leading to a higher likelihood of resignation compared to lower-rated players, who may not fully grasp the inevitability of the outcome and may therefore continue playing.

Additionally, we observed a slight increase in the number of draws and time-out losses as the rating level rises. This phenomenon could be explained by the fact that higher-rated players are more adept at reaching drawn positions or holding out for a time-control victory. As players' understanding of the game deepens, they become better at maneuvering for draws or using their knowledge of time management to secure non-defeat scenarios.

# 6. Conclusion
### Hypothesis 1
This study emphasizes the role of player ratings in shaping chess strategies and decision-making. As players progress in skill, their approach to the game becomes less focused on rote memorization of opening moves and more oriented toward understanding complex positional factors. Future research could further investigate how different time controls influence not only the first-move advantage but also strategic choices across varying skill levels.

### Hypothesis 2
Our analysis confirms the hypothesis that higher-rated players are more likely to resign a game than to be checkmated. This is clearly demonstrated in the Lichess data analysis, which shows a significant correlation between Elo ratings and the likelihood of resignation. Higher-rated players tend to end their games through resignation more often, while lower-rated players are more inclined to play until checkmate.
 
These findings align with expectations and cultural norms in chess, particularly in professional settings, where resignation in lost positions is considered appropriate. At the same time, they highlight behavioral differences across skill levels, which may be attributed to factors such as experience, strategic understanding, and the ability to assess one's position accurately.
 
Overall, the analysis provides strong evidence supporting the hypothesis and illustrates that behavior in online chess games is closely tied to player skill levels.

# Contributors
- Karl Sassie (2362789)
- Florian Heinecke-Drescher (1996696)
- Andreas Kammerer (2213463)
- Hanna Schweig (2488253)

# Literature
